{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-09 wacv_for_review.tex
Final WACV submission

Our approach is similar to that of \cite{ma2015long} in that more than
one KCF is used to address the challenges of single target
tracking. But ours is different from their approach because we do not
use those multiple KCFs together at every frame, but alternatively at
every $k$ frame. It intuitively makes sense to alternatively use
multiple KCFs with different purposes because the appearance of a
target does not change drastically over consecutive image frames. For
most case, even it looks the appearance changes, learning a
correlation filter over consecutive frames would not be much different
from the one learned using the image few or $k$ frames later. Figure
\ref{fig:Filters_Comparison} shows examples supporting this
observation.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from CNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

\begin{comment}
{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) 
why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
\end{comment}
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. Two public datasets were used to evaluate the performance of the
proposed algorithm and found, on average, the performance of the
proposed algorithm is better than those of the existing ones over 5\%
on precision at 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123. Finally, we encoded objects with deep
features to boost tracking performance by $5\%$ on embedded systems
with GPUs.

>>>>

Our approach is similar to that of \cite{ma2015long} in that more than
one KCF is used to address the challenges of single target
tracking. But ours is different from their approach because we do not
use those multiple KCFs together at every frame, but alternatively at
every $k$ frame. It intuitively makes sense to alternatively use
multiple KCFs with different purposes because the appearance of a
target does not change drastically over consecutive image frames. For
most case, even it looks the appearance changes, learning a
correlation filter over consecutive frames would not be substantially different
from the one learned using the image few or $k$ frames later. Figure
\ref{fig:Filters_Comparison} shows examples supporting this
observation.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from a CNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

\begin{comment}
{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) 
why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
\end{comment}
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target’s pixel 
coordinates using evolution of the target’s motion observed over frames.
Two public datasets were used to evaluate the performance of the
proposed algorithm and found, on average, the performance of the
proposed algorithm is better than those of the existing ones over 5\%
on precision at 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123. Finally, we encoded objects with deep
features to boost tracking performance by $5\%$ on embedded systems
with GPUs.
